### 2018-01-15 includes/experiment.tex
Revising paper. Adding figures and tables.

            On this problem set \cvc{} did poorly, but \us{} did well. The graphs in figure X show the performance results for both solvers. We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.

@@

            At this stage it discovers that there is a conflict in one of its equivalence classes, as shown in figure X. After discovering the conflict, the rest of the trace is filled with apparently the same operation repeated hundreds of thousands of times. After this operation is finished, \cvc{} recalls the earlier conflict and returns \texttt{unsat}.

            \us{} showed different behaviour on this problem set. It follows a similar process as \cvc{}, except it does not flatten concatenations. In contrast to \cvc{}, \us{} immediately returns \texttt{unsat} as soon as it verifies consistency of equivalence classes as it constructs them, as shown in figure X.

            {\scriptsize\begin{verbatim}
-------- [str] new_eq_check ../src/smt/theory_str.cpp:1864 ---------
checking whether (str.++ "woof" var2) and (str.++ "meow" var42) can be equal
------------------------------------------------
-------- [str] new_eq_check ../src/smt/theory_str.cpp:1867 ---------
inconsistency detected: (str.++ "woof" var2) cannot be equal to (str.++ "meow" var42)
------------------------------------------------
-------- [str] assert_axiom ../src/smt/theory_str.cpp:179 ---------
asserting (not (= (str.++ "woof" var2) (str.++ "meow" var42)))
------------------------------------------------
            \end{verbatim}}

            {\scriptsize\begin{verbatim}
CONFLICT: Eq engine conflict : (and
(= "woof" (str.++ "woof" lsym_5 ... lsym_5))
(= "" lsym_5)
(= "" var3) ... (= "" var30)
(= (str.++ "woof" var3 ... var30) (str.++ "meow" var43 ... var70))
(= "" var43) ... (= "" var70)
(= "meow" (str.++ "meow" lsym_5 ... lsym_5)))
            \end{verbatim}}

@@

            On this problem set \cvc{} did well, but \us{} did poorly. The graphs in figure X show the performance results for both solvers. We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.

>>>>

            On this problem set \cvc{} did poorly, but \us{} did well. The graphs in Figures~\ref{fig:z3str3-lazy-hard} and ~\ref{fig:cvc4-lazy-hard} show the performance results for both solvers. We produce and analyse the execution trace files both solvers' execution on the problem set.

            \begin{figure}[h]
                \begin{subfigure}{.5\textwidth}
                    \includegraphics[width=\textwidth]{data/graphs/z3str3-lazy-hard.png}
                    \caption{Performance of \us{} on Lazy-Hard}
                    \label{fig:z3str3-lazy-hard}
                \end{subfigure}
                \begin{subfigure}{.5\textwidth}
                    \includegraphics[width=\textwidth]{data/graphs/cvc4-lazy-hard.png}
                    \caption{Performance of \cvc{} on Lazy-Hard}
                    \label{fig:cvc4-lazy-hard}
                \end{subfigure}
            \end{figure}

@@

            At this stage it discovers that there is a conflict in one of its equivalence classes, as shown in Figure~\ref{fig:cvc4-conflict}. After discovering the conflict, the rest of the trace is filled with apparently the same operation repeated hundreds of thousands of times. After this operation is finished, \cvc{} recalls the earlier conflict and returns \texttt{unsat}.

            \us{} showed different behaviour on this problem set. It follows a similar process as \cvc{}, except it does not flatten concatenations. In contrast to \cvc{}, \us{} immediately returns \texttt{unsat} as soon as it verifies consistency of equivalence classes as it constructs them, as shown in Figure~\ref{fig:z3str3-conflict}.

            \begin{figure}[h]
                {\scriptsize\begin{verbatim}
-------- [str] new_eq_check ../src/smt/theory_str.cpp:1864 ---------
checking whether (str.++ "woof" var2) and (str.++ "meow" var42) can be equal
------------------------------------------------
-------- [str] new_eq_check ../src/smt/theory_str.cpp:1867 ---------
inconsistency detected: (str.++ "woof" var2) cannot be equal to (str.++ "meow" var42)
------------------------------------------------
-------- [str] assert_axiom ../src/smt/theory_str.cpp:179 ---------
asserting (not (= (str.++ "woof" var2) (str.++ "meow" var42)))
------------------------------------------------\end{verbatim}}
                \caption{Evidence of \us{} detecting conflict}
                \label{fig:z3str3-conflict}
            \end{figure}

            \begin{figure}[h]
                {\scriptsize\begin{verbatim}
CONFLICT: Eq engine conflict : (and
(= "woof" (str.++ "woof" lsym_5 ... lsym_5))
(= "" lsym_5)
(= "" var3) ... (= "" var30)
(= (str.++ "woof" var3 ... var30) (str.++ "meow" var43 ... var70))
(= "" var43) ... (= "" var70)
(= "meow" (str.++ "meow" lsym_5 ... lsym_5)))\end{verbatim}}
                \caption{Evidence of \cvc{} detecting conflict}
                \label{fig:cvc4-conflict}
            \end{figure}

@@

            On this problem set \cvc{} did well, but \us{} did poorly. The graphs in Figures~\ref{fig:z3str3-eager-hard} and ~\ref{fig:cvc4-eager-hard} show the performance results for both solvers. We produce and analyse the execution trace files both solvers' execution on the problem set, and present them in the Appendix.

            \begin{figure}[h]
                \begin{subfigure}{.5\textwidth}
                    \includegraphics[width=\textwidth]{data/graphs/z3str3-eager-hard.png}
                    \caption{Performance of \us{} on Eager-Hard}
                    \label{fig:z3str3-eager-hard}
                \end{subfigure}
                \begin{subfigure}{.5\textwidth}
                    \includegraphics[width=\textwidth]{data/graphs/cvc4-eager-hard.png}
                    \caption{Performance of \cvc{} on Eager-Hard}
                    \label{fig:cvc4-eager-hard}
                \end{subfigure}
            \end{figure}

### 2018-01-15 includes/introduction.tex
Revising paper. Adding figures and tables.

    \begin{enumerate}
        \item StringFuzzG and StringFuzzX: a generator and transformer of \smt{} string and regex problems.
        \item Experiments on generated inputs that show evidence of poor performance in \us{} and \cvc{}.
        \item A recommended fix to \us{} that alleviates the poor performance.
        \item A large suite of \smt{} string and regex problems we generated with \fuzzer{}.
    \end{enumerate}

>>>>

    \begin{enumerate}
        \item \fuzzer{}: a fuzzer of \smt{} string and regex problems.
        \item Generated inputs that elicit poor performance in \us{} and \cvc{}.
        \item A recommended fix to \us{} that alleviates the poor performance.
        \item A large suite of \smt{} string and regex problems we generated with \fuzzer{}.
    \end{enumerate}

### 2018-01-15 includes/problems.tex
Revising paper. Adding figures and tables.

    \subsection{\fuzzer{}-Generated}

        This suite contains the following problem sets:

        \begin{itemize}
            \item Lengths
            \item Lengths-Concats
            \item Concats
            \item Concats-Extracts
            \item Overlaps
            \item Regex
            \item Many-Regexes
            \item Regex-Deep
            \item Regex-Pair
            \item Regex-Lengths
            \item Random??
        \end{itemize}

        Most of these problem sets either have a dedicated generator in \generator{}, or are variations of one. While it is likely that some of the pre-made suites will be immediately useful in analysing a solver, we also found that mass randomisation was helpful in finding some bugs, and we encourage this pattern as well. \generator{} is designed to be used in an exploratory fashion. For example the following usage has helped us find bugs in \us{}:

\begin{verbatim}
while true; do stringfuzzg --random regex | z3str3 -in; done
\end{verbatim}

    \subsection{\fuzzer{}-Transformed}

        This suite contains the following problem sets:

        \begin{itemize}
            \item Amazon??
            \item Regex??
        \end{itemize}

@@

    \subsection{Unit Tests}

@@

        This section describes the bugs in \us{} that were discovered (and subsequently fixed) by testing it with the \fuzzer{} problem suites.

        \begin{enumerate}
            \item length lookup using eqc root
            \item length-testing bug
        \end{enumerate}

>>>>

    \subsubsection{\fuzzer{}-Generated}

        This suite contains the following problem sets: \\

        \begin{tabular}{|c|c|}
            \hline
            \textbf{Name}    & \textbf{Description} \\ \hline
            Lengths          & \\ \hline
            Lengths-Concats  & \\ \hline
            Concats          & \\ \hline
            Concats-Extracts & \\ \hline
            Overlaps         & \\ \hline
            Regex            & \\ \hline
            Many-Regexes     & \\ \hline
            Regex-Deep       & \\ \hline
            Regex-Pair       & \\ \hline
            Regex-Lengths    & \\ \hline
            Random??         & \\ \hline
        \end{tabular}

        \hfill \\

        Most of these problem sets either have a dedicated generator in \generator{}, or are variations of one. While it is likely that some of the pre-made suites will be immediately useful in analysing a solver, we also found that mass randomisation was helpful in finding some bugs, and we encourage this pattern as well. \generator{} is designed to be used in an exploratory fashion. For example the following usage has helped us find bugs in \us{}: \\

        {\scriptsize\begin{verbatim}
while true; do stringfuzzg --random regex | z3str3 -in; done\end{verbatim}}

    \subsubsection{\fuzzer{}-Transformed}

        This suite contains the following problem sets: \\

        \begin{tabular}{|c|c|}
            \hline
            \textbf{Name} & \textbf{Description} \\ \hline
            Amazon??      & \\ \hline
            Regex??       & \\ \hline
        \end{tabular}

        \hfill \\

@@

    \subsubsection{Unit Tests}

@@

        This section describes the bugs in \us{} that were discovered (and subsequently fixed) by testing it with the \fuzzer{} problem suites, as follows: \\

        \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Name} & \textbf{Description} & \textbf{Before Fix} & \textbf{After Fix} \\ \hline
            length lookup  & & & \\ \hline
            length-testing & & & \\ \hline
        \end{tabular}

### 2018-01-15 includes/stringfuzz.tex
Revising paper. Adding figures and tables.

    This section describes the fuzzer \fuzzer{}. \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems. Its source code repository is available at \sourceRepo{}. It can either be installed from source, or from the Python PIP package repository.

    The \fuzzer{} code is organised to be easily extended with more generators and transformers. It is also implemented in the spirit of a Unix "filter", to be easily integrated into other tools. For example, the outputs of generators can be piped directly into transformers, and transformers can be chained to produce a tuned stream of challenging inputs to a solver.

@@

        \item[\texttt{stringfuzzg}] \hfill \\
            This tool generates \smt{} problems. It supports several generators and options that control its output. The generators it implements are:

            \begin{itemize}
                \item concats
                \item lengths
                \item overlaps
                \item regex
                \item random-text
            \end{itemize}

        \item[\texttt{stringfuzzx}] \hfill \\
            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are:

            \begin{itemize}
                \item fuzz
                \item graft
                \item multiply
                \item nop
                \item reverse
                \item rotate
                \item translate
                \item unprintable
            \end{itemize}

>>>>

    This section describes the fuzzer \fuzzer{}, which generates new \smt{} problems or transforms existing ones. \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smt{} string problems. Its source code repository is available at \sourceRepo{}. It can either be installed from source, or from the Python PIP package repository.

    The \fuzzer{} code is organised to be easily extended: all generators and transformers are independent modules. It is also implemented as a Unix "filter", to enable easy integration with other tools (including itself). For example, the outputs of generators can be piped directly into transformers, and transformers can be chained to produce a tuned stream of challenging inputs to a solver.

@@

        \item[\texttt{stringfuzzg}] \hfill \\
            This tool generates \smt{} problems. It supports several generators and options that control its output. The generators it implements are: \\

            \begin{tabular}{|c|c|}
                \hline
                \textbf{Name} & \textbf{Description} \\ \hline
                concats       & \\ \hline
                lengths       & \\ \hline
                overlaps      & \\ \hline
                regex         & \\ \hline
                random-text   & \\ \hline
            \end{tabular}

            \hfill \\

        \item[\texttt{stringfuzzx}] \hfill \\
            This tool transforms \smt{} problems.. It supports several transformers and options that control its output and input. The transformers it implements are:\\

            \begin{tabular}{|c|c|}
                \hline
                \textbf{Name} & \textbf{Description} \\ \hline
                fuzz          & \\ \hline
                graft         & \\ \hline
                multiply      & \\ \hline
                nop           & \\ \hline
                reverse       & \\ \hline
                rotate        & \\ \hline
                translate     & \\ \hline
                unprintable   & \\ \hline
            \end{tabular}

            \hfill \\
